### 2009-11-19 doc/manuals/janitor/tex_titlepage/titlepage.tex
Michael's bits.
Smallish updates of names and document ID

{\raggedleft NORDUGRID-D2.5-2 ???\par}

@@

%%%%---- The title ----
{\centering \textsc{\Large Dynamic Runtime Environment Installation with Janitor}
\\\vspace{1cm} \normalsize\textcolor{discreeturgent}{This document is still under development, but don't hesitate sending your comments and suggestions to glodek@inb.uni-luebeck.de.} % DELETE ONLY THAT LINE!!!
\Large \par}
\vspace*{0.5cm}

>>>>

{\raggedleft NORDUGRID-MANUAL-11\par}

@@

%%%%---- The title ----
{\centering \textsc{\Large Dynamic Runtime Environments with Janitor}
\\\vspace{1cm} \normalsize\textcolor{discreeturgent}{This document is still under development, but don't hesitate sending your comments and suggestions to moeller@inb.uni-luebeck.de.} % DELETE ONLY THAT LINE!!!
\Large \par}
\vspace*{0.5cm}
